AFQ-Insight

### 2019-12-11 reports/manuscript/sections/conclusion.tex
Incorporates some of Jason's comments/suggestions.

We present here a novel method for analysis of dMRI tractometry data. This
method relies on the Sparse Group Lasso \cite{simon2013sparse} to provide both
accurate prediction of the phenotypic properties of individual subjects based on
their dMRI data, but also provides interpretable results by identifying the
features that are important across subjects to make these predictions. The
method is broadly applicable: it performs well in predicting both continuous
variables, such as biological age, as well as discrete variable, such as whether
a person is a patient or a healthy control. In both of these cases, SGL
out-performs previous algorithms that have been developed for these tasks
\cite{sarica2017corticospinal, Richard2018-ux}. The nested cross-validation
approach used to fit the model and make both predictioons and inferences from it
guards against overfitting and tunes the degree of sparseness required by the
algorithm, such that both phenomena that are locally focused in a particular
anatomical location and a particular property of diffusion (e.g., FA in the
CST), as well as widely distributed phenomena can be accurately captured.

Specifically, we demonstrated that the algorithm correctly detects the fact that
ALS, which is a disease of lower motor neurons, is localized to the
cortico-spinal tract. This recapitulates the results of previous analysis of
these same data, using a targetted ROI-based approach
\cite{sarica2017corticospinal}. In contrast, in analysis of biological age, the
coefficients identified by the algorithm are very widely distributed in many
parts of the white matter, mirroring previous results with this dataset that
show a large and continuous distribution of life-span changes in white matter
properties \cite{yeatman2014lifespan}.

@@

Meanwhile, neuroscience has entered an era in which consortium efforts are
putting together large datasets of high-quality dMRI data to address a variety
of scientific questions \cite{jernigan2016ping, jernigan2018abcd,
alexander2017open, Miller2016-hw, VanEssen2012}. The volume and complexity of
these data pose a substantial challenge. Dimensionality reduction with
tractometry, followed by analysis with the approach we present here promises to
capitalize on the wealth of data and on the co-measurement of interesting and
important phenotypical data about brain health and about the participants'
cognitive abilities. We also expect the group-regularized approach to improve
with larger datasets.

@@

The method is packaged as open-source software called AFQ-Insight that is openly
available, and this also where extensions of the method will be developed. The
sofware integrates within a broader automated fiber quantification software
ecosystem: AFQ \cite{yeatman2012tract}, which extracts tractometry data from raw
and processed dMRI datasets, as well as AFQ-Browser, which visualizes
tractometry data and facilitates sharing of the results of dMRI studies
\cite{yeatman2018browser}. To facilitate reproducibility and ease use of the
software, the results presented in this paper are also provided in
\url{https://github.com/richford/afq-insight-paper} as a series of Jupyter
notebooks
\cite{kluyver2016jupyter}

>>>>

We present here a novel method for analysis of dMRI tractometry data that relies
on the Sparse Group Lasso \cite{simon2013sparse} to (a) make accurate
predictions of phenotypic properties of individual subjects while,
simultaneously, (b) identifying the most important features of the white matter
in a completely data-driven approach. Importantly, through the use of a nested
cross-validation procedure, the method adapts to the constraints of small
datasets while also leveraging the power of larger datasets. Moreover, the
method is broadly applicable to a wide range of research questions: it performs
well in predicting both continuous variables, such as biological age, as well as
categorical variables, such as whether a person is a patient or a healthy control.
In both of these cases, SGL out-performs previous algorithms that have been
developed for these tasks \cite{sarica2017corticospinal, Richard2018-ux}. The
nested cross-validation approach used to fit the model and make both predictions
and inferences from it guards against overfitting and tunes the degree of
sparseness required by the algorithm. This means that both phenomena that are
locally focused in a particular anatomical location and a particular property of
diffusion (e.g., FA in the CST), as well as widely distributed phenomena can be
accurately captured.

Specifically, we demonstrated that the algorithm correctly detects the fact that
ALS, which is a disease of lower motor neurons, is localized to the
cortico-spinal tract. This recapitulates the results of previous analysis of
these same data, using a targetted ROI-based approach
\cite{sarica2017corticospinal}. In contrast, in analysis of biological age, the
coefficients identified by the algorithm are very widely distributed across many
parts of the white matter, mirroring previous results with this dataset that
show a large and continuous distribution of life-span changes in white matter
properties \cite{yeatman2014lifespan}.

@@

Neuroscience has entered an era in which consortium efforts are putting together
large datasets of high-quality dMRI data to address a variety of scientific
questions \cite{jernigan2016ping, jernigan2018abcd, alexander2017open,
Miller2016-hw, VanEssen2012}. The volume and complexity of these data pose a
substantial challenge. Dimensionality reduction with tractometry, followed by
analysis with the approach we present here promises to capitalize on the wealth
of data and on the co-measurement of interesting and important phenotypical data
about brain health and about the participants' cognitive abilities. We also
expect the group-regularized approach to improve with larger datasets.

@@

The method is packaged as open-source software called AFQ-Insight that is openly
available, and provides a clear API to allow for extensions of the method. The
sofware integrates within a broader automated fiber quantification software
ecosystem: AFQ \cite{yeatman2012tract}, which extracts tractometry data from raw
and processed dMRI datasets, as well as AFQ-Browser, which visualizes
tractometry data and facilitates sharing of the results of dMRI studies
\cite{yeatman2018browser}. To facilitate reproducibility and ease use of the
software, the results presented in this paper are also provided in
\url{https://github.com/richford/afq-insight-paper} as a series of Jupyter
notebooks
\cite{kluyver2016jupyter}

### 2019-12-11 reports/manuscript/sections/introduction.tex
Incorporates some of Jason's comments/suggestions.

Diffusion-weighted Magnetic Resonance Imaging (dMRI) provides a unique view into
the physical properties of the connections that comprise the brain white matter
\cite{wandell2016clarifying}. Among the benefits of the method are the fact that
it is non-invasive, and feasible to conduct in clinical scanners, and in wide
variety of populations: healthy adults, but also clinical populations, as well
as young or elderly subjects. While the measurements are usually conducted with
voxels at the millimeter scale, within the diffusion time usually used, water
molecules within each voxel can probe the structure of white matter at the
micrometer scale, providing important information about the physical structure
of the white matter, such as the distribution of fiber orientations within each
voxel \cite{Frank2002-iz, Frank2001-xf}. With more sophisticated measurements
that include several diffusion-weightings, more information can be extracted
about the composition of different tissue type in the voxel
\cite{Jeurissen2014-ab, Kaden2016-ho}. In addition, phenomenological
descriptions of the diffusion properties, such as its mean diffusivity or
fractional anisotropy can be derived from dMRI measurements
\cite{Pierpaoli1996-vj}. Some of these descriptions are ambiguous in terms of
their interpretation, as variance in these properties can relate to several
different underlying physical causes. For example, fractional anisotropy can
decrease both because of demyelination, but also because of decreased density,
or because of partial volume with other tissue types or between crossing fiber
populations \cite{Beaulieu1996-fn, Beaulieu2002-tl}. Even so, these descriptions
have proven useful in characterizing individual differences or differences
between populations \ariel{citation needed}.

To relate the diffusion in each voxel to the macro-structure of long-range
connections between different brain regions, methods for computational
tract-tracing from diffusion MRI, or tractography, combine the estimates of
fiber orientations in each voxel to form streamlines that traverse the volume of
the white matter \cite{Conturo1999-je, Mori2002-qi}. These methods have been
under increased scrutiny and several lines of investigation have raised
critiques of their validity \cite{Maier-Hein2017-vb, Thomas2014-ki}. On the
other hand, there have been efforts to shore up the inferences made with these
methods \cite{Pestilli2014NatMeth, Takemura2016-sh, Smith2013-nc, Smith2015-cx,
Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel fiber
bundles requires extraordinary evidence, and delineating the exact location of
the termination of the streamlines in the gray matter is still prone to error,
there is little dispute that tractography can accurately delineate major white
matter bundles that are known to exist within the core of the white matter
\cite{Maier-Hein2017-vb}.

Using this fact, one of the most powerful methods currently available to put
macro- and micro-structure together is \emph{tractometry} (also known as
tract-based morphometry): assessment of the physical properties of the white
matter along specific tracts \cite{Bells2011-cf}. Though there are several
different available implementations of this overall idea, the principles are
similar \cite{yeatman2012tract, Yendiki2011-ay, Wassermann2016-iv, ODonnell2009-uu}:
tractometry begins by delineating the parts of the white matter that belong to
different major tracts and axonal fiber bundles, such as the corticospinal tract
or arcuate fasciculus, and samples the biophysical properties (such as
fractional anisotropy or mean diffusivity) along the length of these bundles. In
some cases, tissue properties along the length of each bundle are summarized by
taking the mean along each bundle, but there is a large body of evidence showing
that there is systematic variability within each bundle. This justifies
retaining the individual samples along the length of each fiber
\cite{yeatman2012tract, colby2012, ODonnell2009-uu}. While this retains
important information about each individual's white matter, it also presents
statistical challenges due to the dimensionality of the data. Based on
tractometry, researchers may choose to compare different individuals to each
other. This is usually done following one of the following approaches:

@@

\item ROI-based approach: An alternative is using an ROI based approach. In this
approach, the multiple comparison problem is circumvented by selecting just a
few tracts to compare in each individual, or even focusing on particular
segments of these tracts. This approach is very powerful when the biological
basis of the process of interest is relatively well understood (for a recent
example, see \cite{huber2018rapid}).

@@

In the present work, we developed a novel framework for analysis of tractometry
that simultaneously selects the features for analysis, and fits a model to these
features. Rather than a comparative approach, this framework takes a predictive
approach to inference \cite{Breiman2001-uz}. We use a linear modeling approach,
which aims to predict phenotypical variance in a group of subjects, based on a
linear combination of the features estimated with tractometry. Using this
approach, we need to first deal with the large and asymmetric dimensionality of
the data: tractometry data usually has many more features (i.e., number of
measurements per individual) than samples (number of subjects), which makes
inferences from the data about phenotypical differences between individuals
ill-posed. This regime is the target of several statistical learning techniques,
and is often solved by various forms of regularization. For example, Tikhonov
regularization shrinks the solution such that the sum of squared contributions
from the individual features are minimized \cite{Hoerl2000-ij}. Another solution
to the problem is provided by the Lasso algorithm, which instead minimizes the
sum of the absolute values of contributions of each feature
\cite{Tibshirani1996-qs}. This tends to shrink to zero the contributions of many
of the features, providing results that are both accurate and interpretable.
When additional structure is available in the organization of the data,
regularization algorithms can take advantage of this structure. For example, if
the features lend themselves to a natural division into different groups, the
group lasso (GL) can be used to select groups of features, rather than
individual features \cite{Yuan2006-ky}. The Sparse Group Lasso (SGL) elaborates
on this idea by providing control both of group sparsity, as well as overall
sparsity of the solutions \cite{simon2013sgl}. Because the features measured
with tractomery lend themselves to grouping based on the tracts from which each
measurement is taken, GL and SGL provide a useful tool linear model fitting in
problems of this form. Using linear regression as the basis for analysis is
useful for both regression tasks, in which a continuous measure (e.g., age) is
modeled, as well as for classification tasks, where a discrete property is
modeled (e.g., whether an individual has a particular disease). Moreover, use of
SGL helps derive informative properties of the human white matter, both in cases
where the underlying causes of variance are sparsely concentrated (e.g., in one
particular white matter tract) and in cases where biological substrates of
differences between individuals are more widespread. This is because SGL is
controlled by meta-parameters that set the degree to which group sparsity and
overall sparsity are applied. These metaparameters can be set empirically, based
on the data, through a process of nested cross-validation. We demonstrate these
properties of the algorithm in data from previously published studies
\cite{sarica2017corticospinal, yeatman2014lifespan}.

>>>>

Diffusion-weighted Magnetic Resonance Imaging (dMRI) provides a unique view into
the physical properties of the connections that comprise the brain white matter.
While the measurements are usually conducted with voxels at the millimeter
scale, water molecules within each voxel probe the structure of white matter at
the micrometer scale providing important information about the physical
structure of the white matter, including  the distribution of fiber orientations
and density of axons within each voxel \cite{wandell2016clarifying}. Even though
metrics derived from diffusion measurements are ambiguous in terms of their
underlying biological interpretation, analyzing the variance in these properties
has proven useful in characterizing individual differences in cognitive
function, characterizing differences between populations and detecting
abnormalities associated with disease \cite{Thomason2011-qn}

To relate the diffusion in each voxel to the macro-structure of long-range
connections between different brain regions, methods for computational
tract-tracing from diffusion MRI, or tractography, combine the estimates of
fiber orientations in each voxel to form streamlines that traverse the volume of
the white matter \cite{Conturo1999-je, Mori2002-qi}. These methods have been
under increased scrutiny and several lines of investigation have raised
critiques of their validity \cite{Maier-Hein2017-vb, Thomas2014-ki}. On the
other hand, there have been efforts to shore up the inferences made with these
methods \cite{Pestilli2014NatMeth, Takemura2016-sh, Smith2013-nc, Smith2015-cx,
Smith2015-zt, Rheault2018-wk}. Importantly, though discovering novel fiber
bundles requires extraordinary evidence, and delineating the exact cortical
termination of the streamlines in the gray matter is still prone to error, there
is little dispute that tractography can accurately define the location of major
white matter bundles that are known to exist within the core of the white matter
\cite{Maier-Hein2017-vb}.

Using this fact, one of the most powerful methods currently available to put
macro- and micro-structure together is \emph{tractometry} (also known as
tract-based morphometry): assessment of the physical properties of the white
matter along specific tracts \cite{Bells2011-cf}. Though there are several
different available implementations of this overall idea, the principles are
similar \cite{yeatman2012tract, Yendiki2011-ay, Wassermann2016-iv, ODonnell2009-uu}:
tractometry begins by delineating the parts of the white matter that belong to
different major tracts or axonal fiber bundles, such as the corticospinal tract
or arcuate fasciculus, and samples the biophysical properties (such as
fractional anisotropy or mean diffusivity) along the length of these bundles. In
some cases, tissue properties along the length of each bundle are summarized by
taking the mean along each bundle, but there is a large body of evidence showing
that there is systematic variability within each bundle. This justifies
retaining the individual samples along the length of each fiber
\cite{yeatman2012tract, colby2012, ODonnell2009-uu}. While this retains
important information about each individual's white matter, it also presents
statistical challenges due to the dimensionality of the data. Based on
tractometry, researchers may choose to compare different individuals to each
other. This is usually done following one of the following approaches:

@@

\item ROI-based approach: An alternative is using an ROI based approach. In this
approach, the multiple comparison problem is circumvented by selecting just a
few tracts to compare in each individual, or even focusing on particular
segments of these tracts based on \emph{a priori} hypotheses. This approach is
very powerful when the biological basis of the process of interest is relatively
well understood (for a recent example, see \cite{huber2018rapid}).

@@

Ideally, we would like a method that simultaneously capitalizes on all the data
across all tracts to make the best possible prediction, while also retaining and
surfacing spatial information about the locations that are most informative for
a prediction. In the present work, we developed a novel framework for analysis
of tractometry that simultaneously selects the features for analysis, and fits a
model to these features. Rather than a comparative approach, this framework
takes a predictive approach to inference \cite{Breiman2001-uz}. We use a linear
modeling approach, which aims to predict phenotypical variance in a group of
subjects, based on a linear combination of the features estimated with
tractometry. Using this approach, we need to first deal with the large and
asymmetric dimensionality of the data: tractometry data usually has many more
features (i.e., number of measurements per individual) than samples (number of
subjects), which makes inferences from the data about phenotypical differences
between individuals ill-posed. This regime is the target of several statistical
learning techniques, and is often solved by various forms of regularization. For
example, Tikhonov regularization shrinks the solution such that the sum of
squared contributions from the individual features are minimized
\cite{Hoerl2000-ij}. Another solution to the problem is provided by the Lasso
algorithm, which instead minimizes the sum of the absolute values of
contributions of each feature \cite{Tibshirani1996-qs}. This tends to shrink to
zero the contributions of many of the features, providing results that are both
accurate and interpretable. When additional structure is available in the
organization of the data, regularization algorithms can take advantage of this
structure. For example, if the features lend themselves to a natural division
into different groups, the group lasso (GL) can be used to select groups of
features, rather than individual features \cite{Yuan2006-ky}. The Sparse Group
Lasso (SGL) elaborates on this idea by providing control both of group sparsity,
as well as overall sparsity of the solutions \cite{simon2013sgl}. Because the
features measured with tractomery lend themselves to grouping based on the
tracts from which each measurement is taken, GL and SGL provide a useful tool
linear model fitting in problems of this form. Using linear regression as the
basis for analysis is useful for both regression tasks, in which a continuous
measure (e.g., age) is modeled, as well as for classification tasks, where a
discrete property is modeled (e.g., whether an individual has a particular
disease). Moreover, use of SGL helps derive informative properties of the human
white matter, both in cases where the underlying causes of variance are sparsely
concentrated (e.g., in one particular white matter tract) and in cases where
biological substrates of differences between individuals are more widespread.
This is because SGL is controlled by meta-parameters that set the degree to
which group sparsity and overall sparsity are applied. These metaparameters can
be set empirically, based on the data, through a process of nested
cross-validation. We demonstrate these properties of the algorithm in data from
previously published studies \cite{sarica2017corticospinal,
yeatman2014lifespan}.

### 2019-12-11 reports/manuscript/sections/methods.tex
Incorporates some of Jason's comments/suggestions.

Data from both of these studies was processed in a similar manner, using the
Matlab Automated Fiber Quantification toolbox (AFQ) \cite{yeatman2012tract}:
streamlines representing fascicles of white matter nerve fibers were generated
using a determinstic tractography algorithm that follows the prinicpal diffusion
direction of the diffusion tensor in each voxel (STT \cite{basser2000vivo}).
Major tracts were identified using multiple criteria: streamlines are selected
as candidates for inclusion in a bundle of streamlines that represents a tract
if they pass through known inclusion ROIs and do not pass through exclusion ROIs
\cite{wakana2007reproducibility}. In addition, a probabilistic atlas is used to
exclude streamlines which are unlikely to be part of a tract \cite{Hua2008-sh}.
Each streamline is resampled to 100 nodes and the robust mean at each location
is calculated by estimating the 3D covariance of the location of each node and
excluding streamlines that are more than 5 standard deviations from the mean
location in any node. Finally, a tract profile of tissue properties in each
tract was created by interpolating the value of MRI maps of these tissue
properties to the location of the nodes of the resampled streamlines designated
to each tract. In each of 100 nodes, the values are summed across streamlines,
weighting the contribution of each streamline by the inverse of the mahalnobis
distance of the node from the average  of that node across streamlines. This
means that streamlines that are more representative of the tract contribute more
to the tract profile, relative to streamlines that are on the edge of the tract.

@@

Before fitting a model to the data, imputation and standardization are
performed. Missing node values (e.g., in cases where AFQ designates a node as
not-a-number) are imputed via linear interpolation. Care is taken not to
interpolate across the boundaries between different tracts. Some diffusion
metrics will have naturally larger variance than others and may therefore
dominate the objective function and make the SGL estimator unable to learn from
the lower variance metrics. For example, fractional anisotropy (FA) is bounded
between zero and one and could be overwhelmed by an unscaled higher-variance
metric like the mean diffusivity (MD). To prevent this, we use the
\lstinline{StandardScaler} from scikit-learn\cite{scikit-learn}, to remove each
feature's mean and scale it to unit variance. Scaling is performed separately
within each cross-validation set's training or testing data to prevent leakage
of information between the testing and training sets\cite{kaufman2012leakage}.

>>>>

Data from both of these studies was processed in a similar manner, using the
Matlab Automated Fiber Quantification toolbox (AFQ) \cite{yeatman2012tract}:
streamlines representing fascicles of white matter tracts were generated
using a determinstic tractography algorithm that follows the prinicpal diffusion
direction of the diffusion tensor in each voxel (STT \cite{basser2000vivo}).
Major tracts were identified using multiple criteria: streamlines are selected
as candidates for inclusion in a bundle of streamlines that represents a tract
if they pass through known inclusion ROIs and do not pass through exclusion ROIs
\cite{wakana2007reproducibility}. In addition, a probabilistic atlas is used to
exclude streamlines which are unlikely to be part of a tract \cite{Hua2008-sh}.
Each streamline is resampled to 100 nodes and the robust mean at each location
is calculated by estimating the 3D covariance of the location of each node and
excluding streamlines that are more than 5 standard deviations from the mean
location in any node. Finally, a tract profile of tissue properties in each
tract was created by interpolating the value of MRI maps of these tissue
properties to the location of the nodes of the resampled streamlines designated
to each tract. In each of 100 nodes, the values are summed across streamlines,
weighting the contribution of each streamline by the inverse of the mahalnobis
distance of the node from the average  of that node across streamlines. This
means that streamlines that are more representative of the tract contribute more
to the tract profile, relative to streamlines that are on the edge of the tract.

@@

Before fitting a model to the data, imputation and standardization are
performed. Missing node values (e.g., in cases where AFQ designates a node as
not-a-number) are imputed via linear interpolation. Care is taken not to
interpolate across the boundaries between different tracts. Some diffusion
metrics will have naturally larger variance than others and may therefore
dominate the objective function and make the SGL estimator unable to learn from
the lower variance metrics. For example, fractional anisotropy (FA) is bounded
between zero and one and could be overwhelmed by an unscaled higher-variance
metric like the mean diffusivity (MD). To prevent this we remove each feature's
mean and scale it to unit variance (z-score) using the
\lstinline{StandardScaler} from scikit-learn\cite{scikit-learn}. Scaling is
performed separately within each cross-validation set's training or testing data
to prevent leakage of information between the testing and training
sets\cite{kaufman2012leakage}.

### 2019-12-11 reports/manuscript/sections/results.tex
Incorporates some of Jason's comments/suggestions.

To test the performance of SGL in tractometry data in a continuous regression
task, we focus here on the prediction of biological age from the tractometry
data. Prediction of ``brain age'' is a commonly undertaken task. This is both
because it operates on a natural scale, with meaningful and easily understood
units, as well as because predictions of brain age, and deviations from accurate
prediction are diagnostic of overall brain health (for a recent review, see
\cite{Cole2019-rz}). The WH dataset used here contains data from 76 healthy
subjects, ranging between 6 years and 50 years of age
\cite{yeatman2014lifespan}. In this case, biological age was used as the
predicted variable ($y$ in equation \ref{eq:lm}). SGL was fit to
tractometry-extracted features: FA and MD in 20 major brain tracts, with each
tract divided into 100 nodes. To evaluate the fit of the model, we used a nested
cross-validation procedure. In this procedure, batches of subjects are held out.
For each batch (or fold), the model is fully fit without this data. Then, once
the parameters are fixed, the model is inverted to predict the ages of held out
subjects based on the linear coeffiecients and the static non-linearity.
This scheme automatically finds the right level of regularization and
fits the coefficients to the ill-posed linear model, while guarding against
overfitting. SGL accurately predicts the age of the subjects in this procedure,
with a mean absolute error of 3.6 years (Figure \ref{fig:regress-results}, left
panel). This is lower than the results of a recent study that predicted age in a
large sample, based on diffusion MRI features \cite{Richard2018-ux}.
Nevertheless, older subjects have higher residual variance, reflecting the
automatically-chosen log-transformation and implying that brain age becomes more
difficult to predict as we age chronologically (\ref{fig:regress-results}, right
panel). The model weights are distributed over many different tracts and dMRI
tissue properties (Figure \ref{fig:regress-beta} left). This demonstrates that
SGL is not coerced to produce overly sparse results when a more accurate model
requires a dense selection of features. Furthermore, looking closer at a
selection of tracts where high coefficients are found demonstrates that
diffusion properties (FA, in this case) are different in different age groups in
parts of the tracts where these higher coefficients are found (Figure
\ref{fig:regress-beta} right).

>>>>

To test the performance of SGL with tractometry data in a continuous regression
task, we focus here on the prediction of biological age based on tractometry
data. Prediction of ``brain age'' is a commonly undertaken task. This is both
because it operates on a natural scale, with meaningful and easily understood
units, as well as because predictions of brain age, and deviations from accurate
prediction are diagnostic of overall brain health (for a recent review, see
\cite{Cole2019-rz}). The WH dataset used here contains data from 76 healthy
subjects, ranging between 6 years and 50 years of age
\cite{yeatman2014lifespan}. In this case, biological age was used as the
predicted variable ($y$ in equation \ref{eq:lm}). SGL was fit to
tractometry-extracted features: FA and MD in 20 major brain tracts, with each
tract divided into 100 nodes. To evaluate the fit of the model, we used a nested
cross-validation procedure. In this procedure, batches of subjects are held out.
For each batch (or fold), the model is fully fit without this data. Then, once
the parameters are fixed, the model is inverted to predict the ages of held out
subjects based on the linear coeffiecients and the static non-linearity. This
scheme automatically finds the right level of regularization (i.e., sparseness)
and fits the coefficients to the ill-posed linear model, while guarding against
overfitting. SGL accurately predicts the age of the subjects in this procedure,
with a mean absolute error of 3.6 years (Figure \ref{fig:regress-results}, left
panel). This is lower than the results of a recent study that predicted age in a
large sample, based on diffusion MRI features \cite{Richard2018-ux}.
Nevertheless, older subjects have higher residual variance, reflecting the
automatically-chosen log-transformation and implying that brain age becomes more
difficult to predict as we age chronologically (\ref{fig:regress-results}, right
panel). The model weights are distributed over many different tracts and dMRI
tissue properties (Figure \ref{fig:regress-beta} left). This demonstrates that
SGL is not coerced to produce overly sparse results when a more accurate model
requires a dense selection of features. Furthermore, looking closer at a
selection of tracts where high coefficients are found demonstrates that
diffusion properties (FA, in this case) are different in different age groups in
parts of the tracts where these higher coefficients are found (Figure
\ref{fig:regress-beta} right).
